---
title: "Published social network surveys and software"
author: 
  name: "Raffaele Vacca"
  email: "[raffaelevacca.com](https://www.raffaelevacca.com/)"
  affiliation: "University of Milan"
date: '`r Sys.Date()`'
output: 
  html_document:
    theme: flatly
---

<base target="_top"/>

This is a list of 

1. Published social network [surveys](#surveys) with links to questionnaires and codebooks (sorted from most to least recent).
2. Software [programs](#software) for social network data collection. 

This is a work in progress, I appreciate any comments, corrections or suggestions of more surveys and software: you can contribute via [pull requests](https://github.com/raffaelevacca/Open-social-network-surveys) (just add items to `./Data/surveys.csv` or `software.csv`), or by adding a [GitHub issue](https://github.com/raffaelevacca/Open-social-network-surveys) or [contacting me](https://www.raffaelevacca.com/). Note that only surveys with published questionnaire or codebook are included (not necessarily published data).

_[View on GitHub](https://github.com/raffaelevacca/Open-social-network-surveys)_
  
# Surveys

```{r, echo = FALSE, message = FALSE}
library(DT)
library(tidyverse)
library(magrittr)

# Read the data
data.surveys <- read_csv("./Data/surveys.csv")


data.surveys %<>%
  # Extract latest survey year
  mutate(
    max.year = map_dbl(Years, 
                       ~ str_split(.x, ",|-", simplify = TRUE) %>%
                         as.vector %>%
                         as.numeric %>%
                         max
    )
  ) %>%
  # Sort by latest survey year
  arrange(desc(max.year)) %>%
  dplyr::select(-max.year)

# Convert markdown links to html links across all columns
data.surveys %<>%
  mutate(across(everything(),
                ~ str_replace_all(.x,
                                  "\\[([^\\]]+)\\]\\(([^\\)]+)\\)",
                                  "\\<a target=_blank href=\\2>\\1</a>")
  )
  )

# Export to datatable
DT::datatable(data.surveys, escape = FALSE)
```

# Software

```{r, echo=FALSE, message = FALSE}
# Same as above
read_csv("./Data/software.csv") %>%
  mutate(across(everything(),
                ~ str_replace_all(.x,
                            "\\[([^\\]]+)\\]\\(([^\\)]+)\\)",
                            "\\<a target=_blank href=\\2>\\1</a>")
  )
  ) %>%
  DT::datatable(., escape = FALSE)
```